TBD

### 2021-03-10 outputs/paper/paper.Rmd

---
title: "TBD"
subtitle: "TBD"
author: "Yingying Zhou, Yang Wu, Xinyi Xu, Hong Pan"
thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
  toc: FALSE
bibliography: references.bib
editor_options: 
  chunk_output_type: console
---

@@

>>>>

---
title: "TBD"
subtitle: "TBD"
author: "Yingying Zhou, Yang Wu, Xinyi Xu, Hong Pan"
thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
  toc: FALSE
bibliography: references.bib
editor_options: 
  chunk_output_type: inline
---

@@

## Affect Level

### T test 1

```{r}
#video vs control
t1_a<-t.test(na.omit(dat$post_favor_Sanders[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Sanders[dat$treat_control == 1]))

m1_a<-tidy(t1_a,digits=1)

m1_a%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    AVG_affect_video=estimate1,
    AVG_affect_control=estimate2
  )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs control")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```

### T test2
```{r}
#video vs text
t2_a<-t.test(na.omit(dat$post_favor_Sanders[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Sanders[dat$treat_fake_text == 1]))

m2_a<-tidy(t2_a,digits=1)

m2_a%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    AVG_affect_video=estimate1,
    AVG_affect_text=estimate2
  )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs text")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```
### T test3
```{r}
#video vs audio
t3_a<-t.test(na.omit(dat$post_favor_Sanders[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Sanders[dat$treat_fake_audio == 1]))

m3_a<-tidy(t3_a,digits=1)

m3_a%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    AVG_affect_video=estimate1,
    AVG_affect_audio=estimate2
  )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs audio")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```
### T test 4
```{r}
#video vs skit
t4_a<-t.test(na.omit(dat$post_favor_Sanders[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Sanders[dat$treat_skit == 1]))

m4_a<-tidy(t4_a,digits=1)

m4_a%>%
  select(-c(estimate,statistic,parameter))%>%
  rename(
    AVG_affect_video=estimate1,
    AVG_affect_skit=estimate2
  )%>%
  kableExtra::kbl(caption = "T test: Affect level of video vs skit")%>%
  kableExtra::kable_styling(latex_options = "scale_down")%>%# use scale_down option to make the font
  kableExtra::kable_styling(latex_options = c("hold_position"))
```
